Applied Temporal Analysis: A Complete Run of the FraCaS Test Suite

### 2021-03-02 paper2020/paper.tex
tweak

\cite{bernardy_wide-coverage_2019} presented a
logical system for handling 8 of the 9 sections of the FraCaS test
suite, but excluded section 7, suggesting that it requires many
examples that need an \textit{ad hoc} treatment. Here, we took up this
challenge and have shown that a system similar to theirs can be extended to
cover the remaining section of the test suite, without considerably decreasing the performance of the 
rest of the sections. This is indeed a common problem with logical approaches, namely the fact that one can have theoretically motivated implementations of individual phenomena, e.g. anaphora, ellipsis, quantifiers, temporal reference etc., but when one tries to put all these together into a unified system, this proves to be a daunting task. We believe that this paper presents an exception, and provides a system that can deal with all these different semantic phenomena under a unified system with very good results. 
%
We use the same combination of a number of well-studied tools: type
theory, parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). The system achieves an
accuracy of 0.73 on the Temporal Section and 0.81 overall.
One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with anaphora.

>>>>

\citet{bernardy_wide-coverage_2019} presented a
logical system for handling 8 of the 9 sections of the FraCaS test
suite, but excluded section 7, suggesting that it requires many
examples that need an \textit{ad hoc} treatment. Here, we took up this
challenge and have shown that a system similar to theirs can be extended to
cover the remaining section of the test suite, without considerably decreasing the performance of the 
rest of the sections. This is indeed a common problem with logical approaches, namely the fact that one can have theoretically motivated implementations of individual phenomena, e.g. anaphora, ellipsis, quantifiers, temporal reference etc., but when one tries to put all these together into a unified system, this proves to be a daunting task. We believe that this paper presents an exception, and provides a system that can deal with all these different semantic phenomena under a unified system with very good results. 
%
We use the same combination of a number of well-studied tools: type
theory, parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). The system achieves an
accuracy of 0.73 on the Temporal Section and 0.81 overall.
One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with anaphora.
